Epwshiftr: incorporating open data of climate change prediction into \vspace{4pt} building performance simulation for future adaptation and mitigation\\

### 2023-09-07 full-paper/paper.Rmd
paper: update authors

---
title: |
    Epwshiftr: incorporating open data of climate change prediction into
    \vspace{4pt}
    building performance simulation for future adaptation and mitigation
author:
  - name: Hongyuan Jia
    order: 1
    email: hongyuanjia@cqust.edu.cn
    affiliation: |
        Chongqing University of Science and Technology, Chongqing, 401331, People's Republic of China
  - name: Baisong Ning
    order: 2
    email: bsning@foxmail.com
    affiliation: |
        Zhengzhou University, Zhengzhou, Henan Province, 450001, People's Republic of China

@@

This study was funded by Research Foundation of Chongqing University of Science
and Technology (project No. ckrc2021073) and the 111 project (Grant No. B13041),
The authors also thank the support from the Berkeley Education Alliance for
Research in Singapore (BEARS) for the Singapore-Berkeley Building Efficiency and
Sustainability in the Tropics (SinBerBEST) Program and thank Prof. Adrian Chong
(National University of Singapore) for his scientific input during epwshiftr
development.

>>>>

---
title: |
    Epwshiftr: incorporating open data of climate change prediction into
    \vspace{4pt}
    building performance simulation for future adaptation and mitigation
author:
  - name: Hongyuan Jia
    order: 1
    email: hongyuanjia@cqust.edu.cn
    affiliation: |
        School of Civil Engineering and Architecture, Chongqing University of Science and Technology, Chongqing, 401331, People's Republic of China
  - name: Adrian Chong
    order: 2
    email: adrian.chong@nus.edu.sg
    affiliation: |
        Department of the Built Environment, College of Design and Engineering, National University of Singapore, 117566, Singapore
  - name: Baisong Ning
    order: 3
    email: bsning@foxmail.com
    affiliation: |
        School of Civil Engineering, Zhengzhou University, Zhengzhou, Henan Province, 450001, People's Republic of China

@@

This study was funded by Research Foundation of Chongqing University of Science
and Technology (project No. ckrc2021073) and the 111 project (Grant No. B13041),
The authors also thank the support from the Berkeley Education Alliance for
Research in Singapore (BEARS) for the Singapore-Berkeley Building Efficiency and
Sustainability in the Tropics (SinBerBEST) Program.

### 2023-09-07 full-paper/paper.tex
paper: update authors

%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Please keep the \vspace{4pt} at the top
\title{%
Epwshiftr: incorporating open data of climate change prediction into
\vspace{4pt}
building performance simulation for future adaptation and mitigation\\																								% Line 1
%%% Please keep the \vspace{4pt} between lines in the title
} 																																% Line 2
%If there is no second line then just put \phantom{Line 2} here
%%% Change or delete text before "\\" on the lines below to keep the layout but don't remove the "\\"
%%% Do not exceed more than 6 lines for authors and affiliations
\author{																																														% Line 3
     Hongyuan Jia\textsuperscript{1} ,  Baisong Ning\textsuperscript{2} \\
  \parbox{\linewidth}{\centering%
     \textsuperscript{1}Chongqing University of Science and Technology, Chongqing, 401331, People's Republic of China \\ \textsuperscript{2}Zhengzhou University, Zhengzhou, Henan Province, 450001, People's Republic of China \\
  }
  \phantom{Line 8}\\
  \phantom{Line 9}
  } 																																									% Line 9
\date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line														% Line 10
%END OF THE TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

\hypertarget{highlights}{%
\section{Highlights}\label{highlights}}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{climate-scenarios-in-cmip6-scenariomip}{%
\section{Climate scenarios in CMIP6 ScenarioMIP}\label{climate-scenarios-in-cmip6-scenariomip}}

@@

\hypertarget{epwshiftr-a-free-open-source-future-weather-generation-tool-using-cmip6-scenariomip-data}{%
\section{\texorpdfstring{\texttt{epwshiftr}: a free, open-source future weather generation tool using CMIP6 ScenarioMIP data}{epwshiftr: a free, open-source future weather generation tool using CMIP6 ScenarioMIP data}}\label{epwshiftr-a-free-open-source-future-weather-generation-tool-using-cmip6-scenariomip-data}}

@@

\hypertarget{query-scenariomip-gcm-output-using-esgf}{%
\subsection{Query ScenarioMIP GCM output using ESGF}\label{query-scenariomip-gcm-output-using-esgf}}

@@

\hypertarget{gcm-raw-output-data-management}{%
\subsection{GCM raw output data management}\label{gcm-raw-output-data-management}}

@@

\hypertarget{extraction-of-raw-climate-change-data-based-on-geographic-location}{%
\subsection{Extraction of raw climate change data based on geographic location}\label{extraction-of-raw-climate-change-data-based-on-geographic-location}}

@@

\hypertarget{generation-of-future-weather-data-using-morphing-statistical-downscaling}{%
\subsection{Generation of future weather data using morphing statistical downscaling}\label{generation-of-future-weather-data-using-morphing-statistical-downscaling}}

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

This study was funded by Research Foundation of Chongqing University of Science
and Technology (project No.~ckrc2021073) and the 111 project (Grant No.~B13041),
The authors also thank the support from the Berkeley Education Alliance for
Research in Singapore (BEARS) for the Singapore-Berkeley Building Efficiency and
Sustainability in the Tropics (SinBerBEST) Program and thank Prof.~Adrian Chong
(National University of Singapore) for his scientific input during epwshiftr
development.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Please keep the \vspace{4pt} at the top
\title{%
Epwshiftr: incorporating open data of climate change prediction into
\vspace{4pt}
building performance simulation for future adaptation and mitigation\\																								% Line 1
%%% Please keep the \vspace{4pt} between lines in the title
} 																																% Line 2
%If there is no second line then just put \phantom{Line 2} here
%%% Change or delete text before "\\" on the lines below to keep the layout but don't remove the "\\"
%%% Do not exceed more than 6 lines for authors and affiliations
\author{																																														% Line 3
     Hongyuan Jia\textsuperscript{1} ,  Adrian Chong\textsuperscript{2} ,  Baisong Ning\textsuperscript{3} \\
  \parbox{\linewidth}{\centering%
     \textsuperscript{1}School of Civil Engineering and Architecture, Chongqing University of Science and Technology, Chongqing, 401331, People's Republic of China \\ \textsuperscript{2}Department of the Built Environment, College of Design and Engineering, National University of Singapore, 117566, Singapore \\ \textsuperscript{3}School of Civil Engineering, Zhengzhou University, Zhengzhou, Henan Province, 450001, People's Republic of China \\
  }
  \phantom{Line 8}\\
  \phantom{Line 9}
  } 																																									% Line 9
\date{\vspace{-0.5cm}}	% remove default date and replace the Blank 10th line														% Line 10
%END OF THE TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

\section{Highlights}\label{highlights}

@@

\section{Introduction}\label{introduction}

@@

\section{Climate scenarios in CMIP6 ScenarioMIP}\label{climate-scenarios-in-cmip6-scenariomip}

@@

\section{\texorpdfstring{\texttt{epwshiftr}: a free, open-source future weather generation tool using CMIP6 ScenarioMIP data}{epwshiftr: a free, open-source future weather generation tool using CMIP6 ScenarioMIP data}}\label{epwshiftr-a-free-open-source-future-weather-generation-tool-using-cmip6-scenariomip-data}

@@

\subsection{Query ScenarioMIP GCM output using ESGF}\label{query-scenariomip-gcm-output-using-esgf}

@@

\subsection{GCM raw output data management}\label{gcm-raw-output-data-management}

@@

\subsection{Extraction of raw climate change data based on geographic location}\label{extraction-of-raw-climate-change-data-based-on-geographic-location}

@@

\subsection{Generation of future weather data using morphing statistical downscaling}\label{generation-of-future-weather-data-using-morphing-statistical-downscaling}

@@

\section{Conclusion}\label{conclusion}

@@

\section{Acknowledgements}\label{acknowledgements}

This study was funded by Research Foundation of Chongqing University of Science
and Technology (project No.~ckrc2021073) and the 111 project (Grant No.~B13041),
The authors also thank the support from the Berkeley Education Alliance for
Research in Singapore (BEARS) for the Singapore-Berkeley Building Efficiency and
Sustainability in the Tropics (SinBerBEST) Program.
